% David Lopez's Resume
% URL: https://github.com/davelpz/Resume
% Forked from Chris Gibson's resume
% URL: https://github.com/cgibson/Resume
% Which is in turn based on resume tex file by Kamil Wojcicki
% URL: http://linux.dsplabs.com.au/resume-writing-example-latex-template-linux-curriculum-vitae-professional-cv-layout-format-text-p54/

\documentclass[margin,line]{resume}

\usepackage{graphicx}

\begin{document}

\name{\huge \sc{David Lopez}\vspace{2mm}}
{
    \hfill davelpz@gmail.com           \vspace{0mm}\\\vspace{0mm}%
    %\hfill https://github.com/davelpz \vspace{0mm}\\\vspace{-9mm}%
    \hfill 8318 Archwood Circle, Tampa FL, 33615\\\vspace{0mm}%
    \hfill (813) 351-9084 \vspace{0mm}\\\vspace{-9mm}%
}

%\address
%{
%davelpz@gmail.com
%}
%\address
%{
%8318 Archwood Circle\\
%Tampa\\ FL 33615
%}

\begin{resume}

    \vspace{-3mm}

    %__________________________________________________________________________________________________________________
    % Summary
    \section{\mysidestyle \textbf{\large{S}\small{UMMARY}}}

    \textbf{\textsl{Senior Software Engineer}} with 24 years experience  with graphical  user interfaces, user experience design, human factor engineering, and web technologies.  Full stack skills ranging from database design to front end engineering.\vspace{-1mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Professional Experience
    \section{\mysidestyle \textbf{\large{P}\small{ROFESSIONAL} \large{E}\small{XPERIENCE}}}

    % Verizon
    \textbf{\listing Verizon Data Services Inc.} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Member Techincal Staff} \hfill \textbf{September 1997 -- Present}\\
    \textsf{\textmd{Highlights}}\\
    \begin{itemize}
      \item Team Lead for internationally distributed teams: Duties include project planning, scheduling, and using various management tools to control risk and costs.
      \item Developed patented web frameworks currently in use at Verizon.
      \item Recognized by my peers as a subject matter expert in web technologies such as HTML5, CSS3, Javascript, jQuery, Java, SQL, and Unix.
    \item System Designer: Duties included planning, designing architecture, developing, and implementing numerous systems. Focusing on user centered content that meet business and technical requirements.\\\\
      \textbf{Systems \textmd{(some examples)}}
      \begin{itemize}
      \item \textsl{RFDS} - Radio Frequency Design System
      \begin{itemize}
          \item System Architect: Responsible for planning, design, development, and implementation of a web based RFDS. Radio Frequency Engineers use RFDS to reduce the time required to implement cell tower antenna design(s). 
      \end{itemize}
      \item \textsl{Unified Tasking Engine} - Enterprise solution for human tasking
      \begin{itemize}
          \item System Lead: managed an internationally distributed team to maintain a large Oracle Service Oriented Architecture (SOA) Suite solution used to automate ticket assignments of manual processes.
      \end{itemize}
      \item \textsl{Unified User Interface} - Enterprise provisioning portal
      \begin{itemize}
          \item Team Lead: managed an internationally distributed team of engineers to plan, design, develop, and implement a web portal. Worked with user group to gather, validate, and translate requirements into a technical solution.
      \end{itemize}
      \item \textsl{Provisioning Controller} - Enterprise Orchestration
      \begin{itemize}
          \item Team Lead: managed an internationally distributed team of engineers to maintain, re-engineer, and modernize a complex web user interface.
      \end{itemize}
      \item \textsl{Broadband Assignment Activation Inventory System (BAAIS) Video provisioning} - Synchronous Optical Network (SONET) provisioning
      \begin{itemize}
          \item Graphical User Interface Team Lead: Enhanced BAAIS to perform SONET provisioning. Responsible for user interface design and implementation for a interactive web based application.
      \end{itemize}
      \item \textsl{BAAIS} - Digital Subscriber Line (DSL) provisioning
      \begin{itemize}
          \item Module Lead: Enhanced Assignment Activation Inventory System (AAIS) system to perform DSL provisioning. Responsible for system and schema design, data migration, and back-end functionality supporting graphical user interface enhancements.
      \end{itemize}
      \item \textsl{AAIS} - Telephone service provisioning
      \begin{itemize}
          \item Module Lead: responsible for schema design, data migration, and back-end functionality supporting a graphical user interface.
      \end{itemize}
      \end{itemize}
    \end{itemize}

    % Origin
    \textbf{\listing Origin Technologies} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Senior Consultant} \hfill \textbf{September 1994 -- September 1997}\
    \begin{itemize}
        \item Worked on systems for GTE (later acquired by Verizon) as a contractor until hired by GTE.
    \end{itemize}
    

    % IBM
    \textbf{\listing IBM} \vspace{2mm}\\\vspace{1mm}%
    \textsl{Software Engineer} \hfill \textbf{June 1990 -- September 1994}\
    \begin{itemize}
        \item Implemented user interface for the OS/400 C++ debugger.
    \end{itemize}
    

    \vspace{32mm}

\sectionline

    %__________________________________________________________________________________________________________________
    % Skills / Keywords
    \section{\mysidestyle \textbf{\large{S}\small{KILLS} / \large{T}\small{OOLS}}}
    \textbf{OS:} Linux (Red Hat and Debian variants), Mac OS X, Windows \\
    \textbf{Scripting:} Bash and utils (sed, awk, grep), Python, Ruby\\
    \textbf{Backend:} Java (J2EE/Spring Boot), Python (Django), Go, SQL, XML, JSON\\
    \textbf{Frontend:} HTML, CSS (Less and Sass), JavaScript (jQuery, ExtJS)\\
    \textbf{Databases:} Oracle, MySQL, PostgreSQL, Cassandra, SQLite\\
    \textbf{Web Application servers/proxies:} Apache, HAProxy, Nginx, Tomcat, Glassfish, Weblogic\\
    \textbf{Version control systems:} Git, Mercurial, Subversion, CVS\\

\sectionline

    %__________________________________________________________________________________________________________________
    % Patents
    \section{\mysidestyle \textbf{\large{P}\small{ATENTS}}}
    \textsl{8,452,861 B2} -- Broadcast Design For Provisioning Reconfigurable Optical Add/Drop Multiplexer Circuits \hfill \textbf{May 28, 2013}\\\\
    \textsl{Patent pending} -- System For Developing, Testing, Deploying, And Managing Applications In Real-Time\\
    \vspace{-4mm}

\sectionline


    %__________________________________________________________________________________________________________________
    % Education
    \section{\mysidestyle \textbf{\large{E}\small{DUCATION}}}

    \textbf{\listing University of Texas}, El Paso, Texas \vspace{1mm}\\
    \textsl{Graduate Coursework} \hfill \textbf{January 1989 -- June 1990}\vspace{-3mm}\\\vspace{-1mm}%

    \textbf{\listing University of Texas}, El Paso, Texas \vspace{1mm}\\
    \textsl{B.S. in Computer Science} \hfill \textbf{August 1984 -- December 1988}\vspace{-3mm}\\\vspace{-1mm}%

    \vspace{-1mm}


\end{resume}
\end{document}
